MLH1_md

### 2017-08-29 README3.Rmd
updating Rmd page

---
title: "MLH1_md"
author: "April"
date: "August 29, 2017"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
library(plyr) 
library(gplots)
library(ggplot2)
library(knitr) #for md tables 
#read in working environment that was already set
setwd("C:/Users/alpeterson7/Documents/MLH1repo")
load(file="MLH1_data_setup.RData")

##FIX ORDER HERE
MLH1_data$strain<- factor(MLH1_data$strain,levels =c("G", "LEWES",
                                     "WSB", "PWD","MSM","CAST"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)
library(dplyr)
MLH1_data <- MLH1_data %>%
  arrange(strain, sex, mouse) %>%
  mutate(file.name = factor(file.name)) #another category that you want the order to match

@@

#save a figure of boxplots for each mouse
ggplot(MLH1_data, aes(x = mouse, y = nMLH1.foci)) + 
  geom_boxplot(data = MLH1_data, aes(fill = factor(strain), color = factor(sex) ) )

ggsave("boxplots_mice.png")

@@

ggplot(MLH1_by_F_strain, aes(x = mouse, y = nMLH1.foci)) + geom_boxplot(data = MLH1_by_F_strain, aes(fill = factor(strain) ) )
ggsave("Female_boxplots.png")

ggplot(MLH1_by_M_strain, aes(x = mouse, y = nMLH1.foci)) + geom_boxplot(data = MLH1_by_F_strain, aes(fill = factor(strain) ) )
ggsave("Male_boxplots.png")
```

@@

passed_mice_kable
```{r setup, include=FALSE, echo=FALSE}

>>>>

---
title: "MLH1_md"
author: "April"
date: "August 25, 2017"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr) 
library(ggplot2)
```

```{r }

#library(knitr) #for md tables 
#read in working environment that was already set
setwd("C:/Users/alpeterson7/Documents/MLH1repo")
load(file="MLH1_data_setup.RData")

```{r orderdf, echo=FALSE}
##FIX ORDER HERE
MLH1_data$strain<- factor(MLH1_data$strain,levels =c("G", "LEWES",
                                     "WSB", "PWD","MSM","CAST"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)
library(dplyr)
MLH1_data <- MLH1_data %>%
  arrange(strain, sex, mouse) %>%
  mutate(file.name = factor(file.name)) #another category that you want the order to match

@@

@@

ggplot(MLH1_by_F_strain, aes(x = mouse, y = nMLH1.foci)) + geom_boxplot(data = MLH1_by_F_strain, aes(fill = factor(strain) ) )

ggplot(MLH1_by_M_strain, aes(x = mouse, y = nMLH1.foci)) + geom_boxplot(data = MLH1_by_F_strain, aes(fill = factor(strain) ) )
```

### PLOTS

```{r plots, echo=FALSE}
#save a figure of boxplots for each mouse
bb <- ggplot(MLH1_data, aes(x = mouse, y = nMLH1.foci)) + 
  geom_boxplot(data = MLH1_data, aes(fill = factor(strain), color = factor(sex) ) ) 
bb

ff <- ggplot(MLH1_by_F_strain, aes(x = mouse, y = nMLH1.foci)) + geom_boxplot(data = MLH1_by_F_strain, aes(fill = factor(strain) ) )
ff

@@

passed_mice_kable
```{r setup, include=FALSE}
